CGAT In The Hat

### 2012-12-06 paper/paper.tex
Added background section for Aldrin. Finished the first drafts of results/future work. Did some light editing on my stuff.

This paper discusses the progress that has been made this quarter and the future work that 
still needs to be done. The rest of the paper is as follows. Section \ref{sec:motive} discusses the
motivation for creating CGAT. Section \ref{sec:choice} explains why we chose MongoDB
as our backend. Section \ref{sec:implementation} goes into the details of how
our backend and frontend are implemented currently. Section \ref{sec:ui} explains the
various features of our UI. Lastly, section \ref{sec:future} describes the future work still left to
do.

@@

\section{Database Choice}\label{sec:choice}
The choice for backend database was between MySQL, Couchbase, and MongoDB.
We included MySQL in the options because its the standard that small websites tend to use. Then we included both
Couchbase and MongoDB in our considerations because they are popular NoSQL database that are different types of NoSQL
databases. Couchbase is a key-value store unlike MongoDB which is a document-store.

We ended up using MongoDB for several reasons. Firstly, the document structure was extremely helpful when storing
relation. We ended up attaching a lot of data on our relations that would of been a pain to store in SQL but being
able to store the data as complex objects in JSON was super helpful. Secondly, being able to store the data in JSON
(BSON in MongoDB) made it extremely easy to retrieve and use the data in a web application. Because of these two reasons
we narrowed our choices down to MongoDB and Couchbase.

When we were deciding between MongoDB and Couchbase we looked at the features they 
provided and noticed several things. First, Couchbase currently is a pure key-value store it has
no idea what the structure of the value. Unlike MongoDB, which can query for fields inside an 
object specified by a key. This feature of MongoDB makes updating relations (which we 
have a lot of) super easy. Second, Couchbase provides a huge
cluster/map reduce overhead that is not necessary for our data.

@@

\section{Future Work}\label{sec:future}

>>>>

This paper discusses the progress that has been made this quarter and the future work that 
still needs to be done. The rest of the paper is as follows. Section \ref{sec:background} discusses
the common terms and biological meanings used in the project. Section \ref{sec:motive} discusses the
motivation for creating CGAT. Section \ref{sec:choice} explains why we chose MongoDB
as our backend. Section \ref{sec:implementation} goes into the details of how
our backend and frontend are implemented currently. Section \ref{sec:results} discusses
the results of our demo to our customer. Lastly, section \ref{sec:future} 
describes the future work still left to do.

\section{Background}\label{sec:background}

@@

\section{Database Choice}\label{sec:choice}
The choice for backend database was between MySQL, Couchbase, and MongoDB.
We included MySQL in the options because its the standard that websites tend to use. Then we included both
Couchbase and MongoDB in our considerations because they are popular NoSQL database of different types of NoSQL
databases. Couchbase is a key-value store whereas MongoDB which is a document-store.

We ended up using MongoDB for several reasons. First, the document structure was extremely helpful when storing
relations. We ended up attaching a lot of data on our relations that would of been a pain to store in SQL but being
able to store the data as complex objects in JSON was super helpful. Second, being able to store the data in JSON
(BSON in MongoDB) made it extremely easy to retrieve and use the data in a web application. Because of these two reasons
we narrowed our choices down to MongoDB and Couchbase.

When we were deciding between MongoDB and Couchbase we looked at the features they 
provided and noticed several things. First, Couchbase currently is a pure key-value store it has
no idea what the structure of the value. Unlike MongoDB, which can query for fields inside an 
object specified by a key. This feature of MongoDB makes updating relations (which we 
have a lot of) super easy. Second, Couchbase provides a huge
cluster/map reduce overhead that is not necessary for our data. Therefore we choose to use
MongoDB for the CGAT database.

@@

\section{Results}\label{sec:results}
We demoed CGAT to Dr. Anya Goodman on the 19th of November. She was pleased with
the work accomplished so far. But she had numerous recommendations for things to fix and update.
We have taken her ideas and attempted to get as much fixed in the last weeks of the quarter.
Some of the notable fixes were removing some of the "prettiness" from the site, making
buttons look more like buttons, and changing some of the words and terminology used on the site.

\section{Future Work}\label{sec:future}
The future work that is left to be done on CGAT falls into several categories.

\subsection{Missing use cases}
We still need to add some of the main use cases that Dr. Goodman wanted. This includes things like
user leveling and immediate feedback on annotations.

\subsection{Bug fixes}
We know of several bugs that still need to be fixed based on feedback from the demo with
Dr. Goodman.

\subsection{New features}
New features for CGAT will most likely be desired after user feedback.

\subsection{Accessibility}
Need to test the accessibility of the site. This includes things like the color set used
and text size.
